01\_thresholding

### 2018-07-11 papers/manuscripts/supplementary/01_thresholding.tex
mardas

    % Define a nice break command that doesn't care if a line doesn't already
    % exist.
    \def\br{\hspace*{\fill} \\* }
    % Math Jax compatability definitions
    \def\gt{>}
    \def\lt{<}
    % Document parameters
    \title{01\_Thresholding\_local}

@@

    \begin{Verbatim}[commandchars=\\\{\}]
{\color{incolor}In [{\color{incolor}1}]:} \PY{k+kn}{import} \PY{n+nn}{numpy} \PY{k+kn}{as} \PY{n+nn}{np}
        \PY{k+kn}{import} \PY{n+nn}{cv2}
        \PY{k+kn}{from} \PY{n+nn}{utility} \PY{k+kn}{import} \PY{o}{*}
        \PY{k+kn}{import} \PY{n+nn}{matplotlib.pyplot} \PY{k+kn}{as} \PY{n+nn}{plt}
        \PY{k+kn}{from} \PY{n+nn}{iced} \PY{k+kn}{import} \PY{n}{normalization}
        \PY{k+kn}{from} \PY{n+nn}{iced} \PY{k+kn}{import} \PY{n+nb}{filter}
        \PY{k+kn}{import} \PY{n+nn}{os}
        \PY{o}{\PYZpc{}}\PY{k}{load\PYZus{}ext} autoreload
        \PY{o}{\PYZpc{}}\PY{k}{autoreload} 2
        \PY{o}{\PYZpc{}}\PY{k}{pylab} inline
        \PY{n}{pylab}\PY{o}{.}\PY{n}{rcParams}\PY{p}{[}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{figure.figsize}\PY{l+s+s1}{\PYZsq{}}\PY{p}{]} \PY{o}{=} \PY{p}{(}\PY{l+m+mi}{15}\PY{p}{,} \PY{l+m+mi}{9}\PY{p}{)}
\end{Verbatim}

@@

    \begin{Verbatim}[commandchars=\\\{\}]
/home/bzr0014/watson/scripts/virt/local/lib/python2.7/site-packages/IPython/core/magics/pylab.py:161: UserWarning: pylab import has clobbered these variables: ['colors', 'log']
`\%matplotlib` prevents importing * from pylab and numpy
  "\textbackslash{}n`\%matplotlib` prevents importing * from pylab and numpy"

@@

    \subsubsection{Initiating matrices}\label{initiating-matrices}

    \begin{Verbatim}[commandchars=\\\{\}]
{\color{incolor}In [{\color{incolor}2}]:} \PY{n}{chr1} \PY{o}{=} \PY{l+m+mi}{1}
        \PY{n}{chr2} \PY{o}{=} \PY{n}{chr1}
        \PY{k}{print} \PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{chromosome 1: }\PY{l+s+si}{\PYZpc{}s}\PY{l+s+s2}{, chromosome 2: }\PY{l+s+si}{\PYZpc{}s}\PY{l+s+s2}{\PYZdq{}}\PY{o}{\PYZpc{}}\PY{p}{(}\PY{n}{chr1}\PY{p}{,} \PY{n}{chr2}\PY{p}{)}
        \PY{c+c1}{\PYZsh{}print observed\PYZus{}mit\PYZus{}original.shape}
        \PY{n}{mit\PYZus{}original} \PY{o}{=} \PY{n}{readYamlIntensities}\PYZbs{}
        \PY{p}{(}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{../data/GM12878\PYZus{}primary/500kb\PYZus{}resolution\PYZus{}intrachromosomal/chr}\PY{l+s+si}{\PYZpc{}d}\PY{l+s+s1}{/MAPQG0/chr}\PY{l+s+si}{\PYZpc{}d}\PY{l+s+s1}{\PYZus{}500kb.RAWobserved}\PY{l+s+s1}{\PYZsq{}}\PYZbs{}
         \PY{o}{\PYZpc{}}\PY{p}{(}\PY{n}{chr1}\PY{p}{,} \PY{n}{chr1}\PY{p}{)}\PY{p}{,} \PY{l+m+mi}{500000}\PY{p}{)}

        \PY{n}{mit} \PY{o}{=} \PY{n}{readMat}\PY{p}{(}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{../data/extracted\PYZus{}all\PYZus{}contact\PYZus{}MIT/chr\PYZus{}}\PY{l+s+si}{\PYZpc{}02d}\PY{l+s+s2}{\PYZus{}}\PY{l+s+si}{\PYZpc{}02d}\PY{l+s+s2}{\PYZus{}500kb.mat}\PY{l+s+s2}{\PYZdq{}}\PY{o}{\PYZpc{}}\PYZbs{}
                      \PY{p}{(}\PY{n}{chr1}\PY{p}{,} \PY{n}{chr2}\PY{p}{)}\PY{p}{,} \PY{l+s+s2}{\PYZdq{}}\PY{l+s+se}{\PYZbs{}t}\PY{l+s+s2}{\PYZdq{}}\PY{p}{)}
        \PY{n}{call4} \PY{o}{=} \PY{n}{readMat}\PY{p}{(}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{../data/extracted\PYZus{}all\PYZus{}contact\PYZus{}call4/chr\PYZus{}}\PY{l+s+si}{\PYZpc{}02d}\PY{l+s+s2}{\PYZus{}}\PY{l+s+si}{\PYZpc{}02d}\PY{l+s+s2}{\PYZus{}500kb.mat}\PY{l+s+s2}{\PYZdq{}}\PY{o}{\PYZpc{}}\PYZbs{}
                        \PY{p}{(}\PY{n}{chr1}\PY{p}{,} \PY{n}{chr2}\PY{p}{)}\PY{p}{,} \PY{l+s+s2}{\PYZdq{}}\PY{l+s+se}{\PYZbs{}t}\PY{l+s+s2}{\PYZdq{}}\PY{p}{)}
        \PY{n}{rl} \PY{o}{=} \PY{n}{readMat}\PY{p}{(}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{../data/extracted\PYZus{}all\PYZus{}contact\PYZus{}RL/chr\PYZus{}}\PY{l+s+si}{\PYZpc{}02d}\PY{l+s+s2}{\PYZus{}}\PY{l+s+si}{\PYZpc{}02d}\PY{l+s+s2}{\PYZus{}500kb.mat}\PY{l+s+s2}{\PYZdq{}}\PY{o}{\PYZpc{}}\PY{p}{(}\PY{n}{chr1}\PY{p}{,} \PY{n}{chr2}\PY{p}{)}\PY{p}{,} \PY{l+s+s2}{\PYZdq{}}\PY{l+s+se}{\PYZbs{}t}\PY{l+s+s2}{\PYZdq{}}\PY{p}{)}

        \PY{n+nb}{all} \PY{o}{=} \PY{n}{readMat}\PY{p}{(}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{../data/extracted\PYZus{}all\PYZus{}contact\PYZus{}ALL/chr\PYZus{}}\PY{l+s+si}{\PYZpc{}02d}\PY{l+s+s2}{\PYZus{}}\PY{l+s+si}{\PYZpc{}02d}\PY{l+s+s2}{\PYZus{}500kb.mat}\PY{l+s+s2}{\PYZdq{}}\PY{o}{\PYZpc{}}\PY{p}{(}\PY{n}{chr1}\PY{p}{,} \PY{n}{chr2}\PY{p}{)}\PY{p}{,} \PY{l+s+s2}{\PYZdq{}}\PY{l+s+se}{\PYZbs{}t}\PY{l+s+s2}{\PYZdq{}}\PY{p}{)}

        \PY{c+c1}{\PYZsh{}There are some blank rows and columns in the matrix. let\PYZsq{}s remove them.}
        \PY{n}{blankRows4}\PY{p}{,} \PY{n}{blankCols4} \PY{o}{=} \PY{n}{getBlankRowsAndColumns}\PY{p}{(}\PY{n}{mit\PYZus{}original}\PY{p}{)}
        \PY{n}{blankRows0}\PY{p}{,} \PY{n}{blankCols0} \PY{o}{=} \PY{n}{getBlankRowsAndColumns}\PY{p}{(}\PY{n}{mit}\PY{p}{)}
        \PY{n}{blankRows1}\PY{p}{,} \PY{n}{blankCols1} \PY{o}{=} \PY{n}{getBlankRowsAndColumns}\PY{p}{(}\PY{n+nb}{all}\PY{p}{)}
        \PY{n}{blankRows2}\PY{p}{,} \PY{n}{blankCols2} \PY{o}{=} \PY{n}{getBlankRowsAndColumns}\PY{p}{(}\PY{n}{rl}\PY{p}{)}
        \PY{n}{blankRows3}\PY{p}{,} \PY{n}{blankCols3} \PY{o}{=} \PY{n}{getBlankRowsAndColumns}\PY{p}{(}\PY{n}{call4}\PY{p}{)}
        \PY{n}{blankRows} \PY{o}{=} \PY{n}{Set}\PY{p}{(}\PY{p}{[}\PY{p}{]}\PY{p}{)}
        \PY{n}{blankCols} \PY{o}{=} \PY{n}{Set}\PY{p}{(}\PY{p}{[}\PY{p}{]}\PY{p}{)}
        \PY{n}{blankRows}\PY{o}{.}\PY{n}{update}\PY{p}{(}\PY{n}{blankRows0}\PY{p}{)}
        \PY{n}{blankRows}\PY{o}{.}\PY{n}{update}\PY{p}{(}\PY{n}{blankRows1}\PY{p}{)}
        \PY{n}{blankRows}\PY{o}{.}\PY{n}{update}\PY{p}{(}\PY{n}{blankRows2}\PY{p}{)}
        \PY{n}{blankRows}\PY{o}{.}\PY{n}{update}\PY{p}{(}\PY{n}{blankRows3}\PY{p}{)}
        \PY{n}{blankRows}\PY{o}{.}\PY{n}{update}\PY{p}{(}\PY{n}{blankRows4}\PY{p}{)}
        \PY{n}{blankCols}\PY{o}{.}\PY{n}{update}\PY{p}{(}\PY{n}{blankCols0}\PY{p}{)}
        \PY{n}{blankCols}\PY{o}{.}\PY{n}{update}\PY{p}{(}\PY{n}{blankCols1}\PY{p}{)}
        \PY{n}{blankCols}\PY{o}{.}\PY{n}{update}\PY{p}{(}\PY{n}{blankCols2}\PY{p}{)}
        \PY{n}{blankCols}\PY{o}{.}\PY{n}{update}\PY{p}{(}\PY{n}{blankCols3}\PY{p}{)}
        \PY{n}{blankCols}\PY{o}{.}\PY{n}{update}\PY{p}{(}\PY{n}{blankCols4}\PY{p}{)}
        \PY{n}{mit\PYZus{}original} \PY{o}{=} \PY{n}{removeRowsAndColumns}\PY{p}{(}\PY{n}{mit\PYZus{}original}\PY{p}{,} \PY{n}{blankRows}\PY{p}{,} \PY{n}{blankCols}\PY{p}{)}
        \PY{n}{mit} \PY{o}{=} \PY{n}{removeRowsAndColumns}\PY{p}{(}\PY{n}{mit}\PY{p}{,} \PY{n}{blankRows}\PY{p}{,} \PY{n}{blankCols}\PY{p}{)}
        \PY{n+nb}{all} \PY{o}{=} \PY{n}{removeRowsAndColumns}\PY{p}{(}\PY{n+nb}{all}\PY{p}{,} \PY{n}{blankRows}\PY{p}{,} \PY{n}{blankCols}\PY{p}{)}
        \PY{n}{rl} \PY{o}{=} \PY{n}{removeRowsAndColumns}\PY{p}{(}\PY{n}{rl}\PY{p}{,} \PY{n}{blankRows}\PY{p}{,} \PY{n}{blankCols}\PY{p}{)}
        \PY{n}{call4} \PY{o}{=} \PY{n}{removeRowsAndColumns}\PY{p}{(}\PY{n}{call4}\PY{p}{,} \PY{n}{blankRows}\PY{p}{,} \PY{n}{blankCols}\PY{p}{)}
\end{Verbatim}

    \begin{Verbatim}[commandchars=\\\{\}]
chromosome 1: 1, chromosome 2: 1
file directory: ../data/extracted\_all\_contact\_MIT/chr\_01\_01\_500kb.mat
file directory: ../data/extracted\_all\_contact\_call4/chr\_01\_01\_500kb.mat
file directory: ../data/extracted\_all\_contact\_RL/chr\_01\_01\_500kb.mat
file directory: ../data/extracted\_all\_contact\_ALL/chr\_01\_01\_500kb.mat
size of old matrix: (499, 499)
size of new matrix: (456, 456)
size of old matrix: (495, 495)
size of new matrix: (452, 452)
size of old matrix: (495, 495)
size of new matrix: (452, 452)
size of old matrix: (495, 495)
size of new matrix: (452, 452)
size of old matrix: (495, 495)
size of new matrix: (452, 452)

@@

    \subsubsection{Comparing MIT with the Rao et al high-resolution
data:}\label{comparing-mit-with-the-rao-et-al-high-resolution-data}

    \begin{Verbatim}[commandchars=\\\{\}]
{\color{incolor}In [{\color{incolor}12}]:} \PY{n}{pylab}\PY{o}{.}\PY{n}{rcParams}\PY{p}{[}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{figure.figsize}\PY{l+s+s1}{\PYZsq{}}\PY{p}{]} \PY{o}{=} \PY{p}{(}\PY{l+m+mi}{15}\PY{p}{,} \PY{l+m+mi}{20}\PY{p}{)}
         \PY{n}{k} \PY{o}{=} \PY{p}{(}\PY{l+m+mi}{2}\PY{p}{,} \PY{l+m+mi}{2}\PY{p}{,} \PY{l+m+mi}{2}\PY{p}{,} \PY{l+m+mi}{2}\PY{p}{)}
         \PY{n}{method} \PY{o}{=} \PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{max}\PY{l+s+s1}{\PYZsq{}}
         \PY{n}{t} \PY{o}{=} \PY{l+m+mi}{0}
         \PY{n}{params} \PY{o}{=} \PY{n+nb+bp}{None}
         \PY{n}{symmetric}\PY{o}{=}\PY{n+nb+bp}{True}
         \PY{n}{call4\PYZus{}os} \PY{o}{=} \PY{n}{local\PYZus{}threshold}\PY{p}{(}\PY{p}{(}\PY{p}{(}\PY{n}{call4}\PY{o}{+}\PY{l+m+mi}{1}\PY{o}{+}\PY{l+m+mf}{1e\PYZhy{}5}\PY{p}{)}\PY{p}{)}\PY{p}{,} \PY{n}{k} \PY{o}{=} \PY{n}{k}\PY{p}{,} \PY{n}{method}\PY{o}{=}\PY{n}{method}\PY{p}{,} \PY{n}{t} \PY{o}{=} \PY{n}{t}\PY{p}{,} \PY{n}{params}\PY{o}{=}\PY{n}{params}\PY{p}{,} \PY{n}{symmetric}\PY{o}{=}\PY{n}{symmetric}\PY{p}{)}
         \PY{n}{rl\PYZus{}os} \PY{o}{=} \PY{n}{local\PYZus{}threshold}\PY{p}{(}\PY{p}{(}\PY{p}{(}\PY{n}{rl}\PY{o}{+}\PY{l+m+mi}{1}\PY{o}{+}\PY{l+m+mf}{1e\PYZhy{}5}\PY{p}{)}\PY{p}{)}\PY{p}{,} \PY{n}{k} \PY{o}{=} \PY{n}{k}\PY{p}{,} \PY{n}{method}\PY{o}{=}\PY{n}{method}\PY{p}{,} \PY{n}{t} \PY{o}{=} \PY{n}{t}\PY{p}{,} \PY{n}{params}\PY{o}{=}\PY{n}{params}\PY{p}{,} \PY{n}{symmetric}\PY{o}{=}\PY{n}{symmetric}\PY{p}{)}
         \PY{n}{n1}\PY{p}{,} \PY{n}{m1} \PY{o}{=} \PY{n}{call4\PYZus{}os}\PY{o}{.}\PY{n}{shape}
         \PY{n}{n2}\PY{p}{,} \PY{n}{m2} \PY{o}{=} \PY{n}{rl\PYZus{}os}\PY{o}{.}\PY{n}{shape}
         \PY{n}{n} \PY{o}{=} \PY{n}{np}\PY{o}{.}\PY{n}{min}\PY{p}{(}\PY{p}{[}\PY{n}{n1}\PY{p}{,} \PY{n}{n2}\PY{p}{]}\PY{p}{)}
         \PY{n}{m} \PY{o}{=} \PY{n}{np}\PY{o}{.}\PY{n}{min}\PY{p}{(}\PY{p}{[}\PY{n}{m1}\PY{p}{,} \PY{n}{m2}\PY{p}{]}\PY{p}{)}
         \PY{n}{call4\PYZus{}os} \PY{o}{=} \PY{n}{call4\PYZus{}os}\PY{p}{[}\PY{p}{:}\PY{n}{n}\PY{p}{,} \PY{p}{:}\PY{n}{m}\PY{p}{]}
         \PY{n}{call4} \PY{o}{=} \PY{n}{call4}\PY{p}{[}\PY{p}{:}\PY{n}{n}\PY{p}{,} \PY{p}{:}\PY{n}{m}\PY{p}{]}
         \PY{n}{rl\PYZus{}os} \PY{o}{=} \PY{n}{rl\PYZus{}os}\PY{p}{[}\PY{p}{:}\PY{n}{n}\PY{p}{,} \PY{p}{:}\PY{n}{m}\PY{p}{]}
         \PY{n}{rl} \PY{o}{=} \PY{n}{rl}\PY{p}{[}\PY{p}{:}\PY{n}{n}\PY{p}{,} \PY{p}{:}\PY{n}{m}\PY{p}{]}
         \PY{n}{a} \PY{o}{=} \PY{p}{(}\PY{p}{(}\PY{n}{call4\PYZus{}os} \PY{o}{*} \PY{n}{call4}\PY{p}{)} \PY{o}{\PYZgt{}} \PY{l+m+mi}{0}\PY{p}{)} \PY{o}{*} \PY{l+m+mi}{1}
         \PY{n}{b} \PY{o}{=} \PY{p}{(}\PY{p}{(}\PY{n}{rl\PYZus{}os} \PY{o}{*} \PY{n}{rl}\PY{p}{)} \PY{o}{\PYZgt{}} \PY{l+m+mi}{0}\PY{p}{)} \PY{o}{*} \PY{l+m+mi}{1}
\end{Verbatim}

>>>>

    % Define a nice break command that doesn't care if a line doesn't already
    % exist.
    \def\br{\hspace*{\fill} \\* }
    % Math Jax compatability definitions
    \def\gt{>}
    \def\lt{<}
    % Document parameters
    \title{01\_thresholding}

@@

    \begin{Verbatim}[commandchars=\\\{\}]
{\color{incolor}In [{\color{incolor}1}]:} \PY{k+kn}{import} \PY{n+nn}{numpy} \PY{k+kn}{as} \PY{n+nn}{np}
        \PY{k+kn}{import} \PY{n+nn}{cv2}
        \PY{k+kn}{from} \PY{n+nn}{library.utility} \PY{k+kn}{import} \PY{o}{*}
        \PY{k+kn}{import} \PY{n+nn}{matplotlib.pyplot} \PY{k+kn}{as} \PY{n+nn}{plt}
        \PY{k+kn}{from} \PY{n+nn}{iced} \PY{k+kn}{import} \PY{n}{normalization}
        \PY{k+kn}{from} \PY{n+nn}{iced} \PY{k+kn}{import} \PY{n+nb}{filter}
        \PY{k+kn}{from} \PY{n+nn}{sets} \PY{k+kn}{import} \PY{n}{Set}
        \PY{k+kn}{import} \PY{n+nn}{os}
        \PY{o}{\PYZpc{}}\PY{k}{load\PYZus{}ext} autoreload
        \PY{o}{\PYZpc{}}\PY{k}{autoreload} 2
        \PY{o}{\PYZpc{}}\PY{k}{pylab} inline
\end{Verbatim}

@@

    \begin{Verbatim}[commandchars=\\\{\}]
/home/bzr0014/git/watson/virt/local/lib/python2.7/site-packages/IPython/core/magics/pylab.py:161: UserWarning: pylab import has clobbered these variables: ['colors', 'log']
`\%matplotlib` prevents importing * from pylab and numpy
  "\textbackslash{}n`\%matplotlib` prevents importing * from pylab and numpy"

@@

    \section{Loading Data}\label{loading-data}

The first step is to load the raw Hi-C contact maps. We have already
extracted all inter- and intra-chromosomal contact maps and compiled
them into as single large numpy array format.

    \begin{Verbatim}[commandchars=\\\{\}]
{\color{incolor}In [{\color{incolor}2}]:} \PY{n}{pylab}\PY{o}{.}\PY{n}{rcParams}\PY{p}{[}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{figure.figsize}\PY{l+s+s1}{\PYZsq{}}\PY{p}{]} \PY{o}{=} \PY{p}{(}\PY{l+m+mi}{15}\PY{p}{,} \PY{l+m+mi}{9}\PY{p}{)}

        \PY{n}{lengths\PYZus{}low\PYZus{}res} \PY{o}{=} \PY{n}{np}\PY{o}{.}\PY{n}{load}\PY{p}{(}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{../numpy\PYZus{}data/length\PYZus{}low\PYZus{}res.npy}\PY{l+s+s1}{\PYZsq{}}\PY{p}{)}
        \PY{n}{mit\PYZus{}full}  \PY{o}{=} \PY{p}{(}\PY{n}{np}\PY{o}{.}\PY{n}{load}\PY{p}{(}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{../numpy\PYZus{}data/mit\PYZus{}low\PYZus{}res.npy}\PY{l+s+s1}{\PYZsq{}}\PY{p}{)}\PY{p}{)}
        \PY{n}{all\PYZus{}full}  \PY{o}{=} \PY{p}{(}\PY{n}{np}\PY{o}{.}\PY{n}{load}\PY{p}{(}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{../numpy\PYZus{}data/all\PYZus{}low\PYZus{}res.npy}\PY{l+s+s1}{\PYZsq{}}\PY{p}{)}\PY{p}{)}
        \PY{n}{rl\PYZus{}full}  \PY{o}{=} \PY{p}{(}\PY{n}{np}\PY{o}{.}\PY{n}{load}\PY{p}{(}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{../numpy\PYZus{}data/rl\PYZus{}low\PYZus{}res.npy}\PY{l+s+s1}{\PYZsq{}}\PY{p}{)}\PY{p}{)}
        \PY{n}{call4\PYZus{}full}  \PY{o}{=} \PY{p}{(}\PY{n}{np}\PY{o}{.}\PY{n}{load}\PY{p}{(}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{../numpy\PYZus{}data/call4\PYZus{}low\PYZus{}res.npy}\PY{l+s+s1}{\PYZsq{}}\PY{p}{)}\PY{p}{)}
        \PY{n}{data} \PY{o}{=} \PY{p}{\PYZob{}}\PY{p}{\PYZcb{}}
        \PY{n}{showImages}\PY{p}{(}\PY{p}{[}\PY{n}{mit\PYZus{}full} \PY{p}{,} \PY{n}{all\PYZus{}full} \PY{p}{,} \PY{n}{rl\PYZus{}full} \PY{p}{,} \PY{n}{call4\PYZus{}full} \PY{p}{]}\PY{p}{,} \PY{n}{rows}\PY{o}{=}\PY{l+m+mi}{2}\PY{p}{,} \PY{n}{titles}\PY{o}{=}\PY{p}{[}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{MIT}\PY{l+s+s1}{\PYZsq{}}\PY{p}{,} \PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{ALL}\PY{l+s+s1}{\PYZsq{}}\PY{p}{,} \PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{RL}\PY{l+s+s1}{\PYZsq{}}\PY{p}{,} \PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{CALL4}\PY{l+s+s1}{\PYZsq{}}\PY{p}{]}\PY{p}{)}
\end{Verbatim}

    \begin{Verbatim}[commandchars=\\\{\}]
Number of rows and columns: 2, 2
(4, 4)

@@

    \begin{center}
    \adjustimage{max size={0.9\linewidth}{0.9\paperheight}}{output_3_1.png}
    \end{center}
    { \hspace*{\fill} \\}

    \section{Selecting a inter-/intra-chromosomal contact
map}\label{selecting-a-inter-intra-chromosomal-contact-map}

You can chang chr1 and chr2 variables based on the contact map you want
to investigate.

    \begin{Verbatim}[commandchars=\\\{\}]
{\color{incolor}In [{\color{incolor}3}]:} \PY{n}{chr1} \PY{o}{=} \PY{l+m+mi}{1}
        \PY{n}{chr2} \PY{o}{=} \PY{l+m+mi}{2}
        \PY{n}{data}\PY{p}{[}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{MIT}\PY{l+s+s1}{\PYZsq{}}\PY{p}{]}          \PY{o}{=} \PY{n}{get\PYZus{}contact\PYZus{}map}\PY{p}{(}\PY{n}{mit\PYZus{}full}        \PY{p}{,} \PY{n}{lengths\PYZus{}low\PYZus{}res}\PY{p}{,} \PY{n}{chr1}\PY{p}{,} \PY{n}{chr2}\PY{p}{)}
        \PY{n}{data}\PY{p}{[}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{ALL}\PY{l+s+s1}{\PYZsq{}}\PY{p}{]}          \PY{o}{=} \PY{n}{get\PYZus{}contact\PYZus{}map}\PY{p}{(}\PY{n}{all\PYZus{}full}        \PY{p}{,} \PY{n}{lengths\PYZus{}low\PYZus{}res}\PY{p}{,} \PY{n}{chr1}\PY{p}{,} \PY{n}{chr2}\PY{p}{)}
        \PY{n}{data}\PY{p}{[}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{RL}\PY{l+s+s1}{\PYZsq{}}\PY{p}{]}           \PY{o}{=} \PY{n}{get\PYZus{}contact\PYZus{}map}\PY{p}{(}\PY{n}{rl\PYZus{}full}         \PY{p}{,} \PY{n}{lengths\PYZus{}low\PYZus{}res}\PY{p}{,} \PY{n}{chr1}\PY{p}{,} \PY{n}{chr2}\PY{p}{)}
        \PY{n}{data}\PY{p}{[}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{CALL4}\PY{l+s+s1}{\PYZsq{}}\PY{p}{]}        \PY{o}{=} \PY{n}{get\PYZus{}contact\PYZus{}map}\PY{p}{(}\PY{n}{call4\PYZus{}full}      \PY{p}{,} \PY{n}{lengths\PYZus{}low\PYZus{}res}\PY{p}{,} \PY{n}{chr1}\PY{p}{,} \PY{n}{chr2}\PY{p}{)}
        \PY{n}{showImages}\PY{p}{(}\PY{n}{data}\PY{p}{,} \PY{n}{rows} \PY{o}{=} \PY{l+m+mi}{2}\PY{p}{,} \PY{n}{titles}\PY{o}{=}\PY{p}{[}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{MIT}\PY{l+s+s1}{\PYZsq{}}\PY{p}{,} \PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{ALL}\PY{l+s+s1}{\PYZsq{}}\PY{p}{,} \PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{RL}\PY{l+s+s1}{\PYZsq{}}\PY{p}{,} \PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{CALL4}\PY{l+s+s1}{\PYZsq{}}\PY{p}{]}\PY{p}{)}
\end{Verbatim}

    \begin{Verbatim}[commandchars=\\\{\}]
Number of rows and columns: 2, 2
(4, 4)

    \begin{center}
    \adjustimage{max size={0.9\linewidth}{0.9\paperheight}}{output_5_1.png}
    \end{center}
    { \hspace*{\fill} \\}

    \subsection{Cleaning Data}\label{cleaning-data}

As can be observed above, there are several rows and columns that simply
don't contain any data and are all zeros, in the following code we clean
the matrices to remove these zero rows and columns since they will cause
problems in future analysis.
